---
title: "ST2195 Scrapping"
author: "Shaniah Santiago"
date: "2025-10-07"
output: html_document
---
## Scraping Website
### Installing Necessary Packages
```{r}
if (!("revest" %in% installed.packages())){
  install.packages("rvest")
}
```
### Library
```{r}
library(rvest)
library(stringr)
```

## Website
```{r}
sim_url <- "https://www.sim.edu.sg/"
sim_web <- read_html(sim_url) ## Reading as a html document and initializing it in sim_web
```

## Finding Contacts and Retrieving Text
Locate the "contact-item" anchors inside "footer" and retrieve only the text
```{r}
sim_contacts <- sim_web %>% 
                #html_nodes(xpath = '//footer//div[contains(@class,"contact-item")]/span[2]') %>% html_text()
                html_elements(xpath='//footer//div[contains(@class, "contact-item")]//span') %>% html_text()

sim_contacts
```

### Cleaning Contacts
Use grepl for partial comparison
Using stringr package to format texts and manipulate string text to retrieve the relevant contact information.
```{r}
# #Remove "Getting Here"
# sim_contacts <- gsub("Getting here", "", sim_contacts)
# 
# #Remove empty strings
# sim_contacts <- sim_contacts[nchar(sim_contacts) > 0] 
# 
# sim_contacts

contact_vec = c()
index <-1
for (item in sim_contacts) {
  if (grepl("email", tolower(item))) {
    email <- sim_contacts[index+1]
    email <- str_trim(email)
    print(email)
    contact_vec = c(contact_vec, email)
  }
  
  if(grepl("phone", tolower(item))){
    phone <- sim_contacts[index+1]
    phone <- str_trim(phone)
    
    #Retrieve only 8 Digits
    phone <- substr(phone, 1,9)
    
    print(phone)
    contact_vec = c(contact_vec, phone)
  }
  
  if(grepl("address", tolower(item))){
    address <- sim_contacts[index+1]
    address <- str_trim(address)
    
    #Retrieiving only address
    pos <- regexpr("Singapore", address)
    address <- substr(address,1 , pos+15)
    
    print(address)
    contact_vec = c(contact_vec, address)
  }
  
  index <- index +1
}

```

### Check Contact List
```{r}
contact_vec
```

## Saving to CSV File
```{r}
write.table(contact_vec, "sim_Contact_Info.csv", sep=",", row.names=FALSE, col.names=FALSE, quote=FALSE)
```

### Check CSV File Exists and Includes Information
```{r}
read.csv("sim_Contact_Info.csv", header=FALSE)
```

