---
title: "titanic"
output: html_document
---
Setting Up Environment
```{r}
#install.packages("ggplot2")
```

### Steps to Resolve Issue with ggplot2
1. Run "install.packages(c("rlang", "vctrs", "cli", "ggplot2"))"
2. Rerun all code chunks
3. Issue arises: "rlang 1.1.6 is already loaded, 1.1.7 is required"
4. Restart R: Session -> Restart R
5. Run code in R terminal
```{r}
#install.packages(c("rlang", "vctrs", "cli", "ggplot2"))
#install.packages("rlang")
#install.packages("ggplot2")
#library(ggplot2)
```


```{r}
library(ggplot2)
library(dplyr)
```

Initializing Data
```{r}
df <- read.csv("titanic.csv")
head(df)
```

Calculate Family Size
Adding Siblings/spouses and number of parents or children onboard Titanic
```{r}
df$family_size <- df$SibSp + df$Parch+1
df
```


Generate a series of bar charts to describe the gender, ticket class and survival of the passengers onboard
```{r}
gender_bar <- ggplot(df) + aes(x=Sex, fill=Sex) + geom_bar() + labs(title = "Gender of Passengers Onboard")
gender_bar
```

```{r}
df %>%
  mutate(Pclass = factor(x=Pclass, levels=c(1,2,3), 
                         labels=c("1st","2nd","3rd"))) %>%
  ggplot(aes(x=Pclass, fill=Pclass)) + 
  geom_bar() + 
  ggtitle("Ticket class of the passengers onboard") + 
  xlab("Ticket Class") +
  theme(legend.position="none")
```

```{r}
df %>% mutate(Survived=factor(x=Survived, levels=c(0,1), labels=c("No","Yes"))) %>% ggplot(aes(x=Survived, fill=Survived)) + geom_bar() + ggtitle("Survival of Passengers Onboard") + theme(legend.position = "none")
```

Generate a histogram for the passengers’ age. Furthermore, describe the passengers’ age using the following two boxplots: age per ticket class and age based on survival.

```{r}
age_hist <- ggplot(df) + aes(x=Age, y=..density..) + geom_histogram(fill="hotpink", bins=20, na.rm=TRUE) + ggtitle("Distribution of Age of Passengers Onboard")

age_hist
```
```{r}
df %>%
  mutate(Pclass=factor(x=Pclass,levels=c(1,2,3), labels=c("1st","2nd","3rd"))) %>%
  ggplot(aes(x=Pclass, y=Age, fill=Pclass)) + geom_boxplot(na.rm=TRUE) +
  ggtitle("Age of Passengers Onboard") +
  xlab("Ticket Class") +
  theme(legend.position = "none")
```
```{r}
df %>%
  mutate(Survived = factor(x=Survived, levels=c(0,1), labels=c("No","Yes"))) %>%
  ggplot(aes(x=Survived, y=Age, fill=Survived)) + geom_boxplot(na.rm=TRUE) + 
  ggtitle("Age of Passengers Onboard") +
  theme(legend.position = "none")
```
Generate a histogram for the travel fare and a table showing the number 
of people who did not pay
```{r}
fare_hist <- ggplot(df) +
  aes(x=Fare, y=..density..) +
  geom_histogram(fill="lightgreen", bins=30, na.rm=TRUE) +
  ggtitle("Ticket Fare of Passengers Onboard")

fare_hist
```
Table showing the number of people who did not pay
```{r}
paid <- table(df$Fare !=0)
names(paid) <- c("Not Paid", "Paid")
paid
```
A chart of your choice to describe the family size per ticket class 
```{r}
df %>% 
  mutate(Pclass=factor(x=Pclass, levels=c(1,2,3), labels=c("1st","2nd","3rd"))) %>%
  ggplot(aes(x=family_size, y=..density.., fill=Pclass)) +
  geom_histogram(bins=11) +
  facet_grid(Pclass ~ ., scales="free") +
  guides(fill=FALSE) +
  ggtitle("Family Size Per Ticket Class")
```

A series of stacked bar charts to show the how survival differs for different gender and ticket class
i. A series of stacked bar charts to show the how survival differs for different gender 
```{r}
df %>% 
  mutate(Survived=factor(x=Survived, levels=c(0,1), labels=c("No","Yes"))) %>% 
  ggplot(aes(fill=Survived, x=Sex)) +
  geom_bar(position="stack") +
  ggtitle("Survival By Gender") +
  xlab("Gender") +
  guides(fill=guide_legend("Survival"))
```
ii. A series of stacked bar charts to show the how survival differs for different ticket class 
```{r}
df %>%
  mutate(Survived=factor(x=Survived, levels=c(0,1), labels=c("No","Yes"))) %>%
  mutate(Pclass=factor(x=Pclass, levels=c(1,2,3), labels=c("1st", "2nd","3rd"))) %>%
  ggplot(aes(fill=Survived, x=Pclass)) +
  geom_bar(position="stack") +
  ggtitle("Survival by Ticket Class") +
  xlab("Ticket Class") +
  guides(fill=guide_legend("Survival"))
```

A violin chart describing how survival related to age and gender 
na.rm=TRUE: does not include any missing or NA values in the count.
```{r}
df %>% 
  mutate(Survived=factor(x=Survived, levels=c(0,1), labels=c("No","Yes"))) %>%
  ggplot(aes(x=Sex, y=Age, fill=Survived)) +
  geom_violin(na.rm=TRUE, adjust=0.5)
```

A violin chart describing the survival rate related to age and ticket class
1. Initialise dataframe to use, titanic
2. Specify Survival Categorical value
3. Change Pclass to Categorical value
4. Plot parameters x-axis, y-axis, and value
5. Specify plot diagram to use
6. Add caption of xaxis of the plot diagram
```{r}
df %>%
  mutate(Survived=factor(x=Survived, levels=c(0,1), labels=c("No", "Yes"))) %>%
  mutate(Pclass=factor(x=Pclass, levels=c(1,2,3), labels=c("1st","2nd","3rd"))) %>%
  ggplot(aes(x=Pclass, y=Age, fill=Survived)) +
  geom_violin(na.rm=TRUE, adjust=0.5) +
  xlab("Ticket Class")
```

