---
title: "ST2195 Practice Assignment"
author: "Shaniah Santiago"
date: "2025-11-25"
output: html_document
---
# foo.R
```{r}
# Radius
r <- 2

# Function to Compute the volume of a sphere with radius r
volume <- function(r, rho){
  3/4*pi*r^2
}

# Function to compute the volumes of the spheres with radius r, r^2, and r^3
volume_vector <- function(r) {
  r <- 22
  for (r in 2:3) {
    volume(r)
  }
}

# Run volume_vector(r) and print the volumes of the sphere with radius r, r^2, and r^3
volume_vector(r)
```

# Fix all the bugs in the code
## Function to Compute the volume of a sphere with radius r
In the original function, 
(1) rho is not used, there it is not necessary in the argument
(2) equation for the volume of sphere is incorrect. Proper volume of sphere equation = 4/3*pi*r^3

```{r}
volume <- function(r){
  4/3*pi*r^3
}
```

## Function to Compute the volumes of the spheres with radius r, r^2, and r^3
In the original function,
(1) A local r variable is initialised. For the argument r to be used, instead of the local r, it needs to be removed.
(2) the powers to be used are 1,2,3, the loop should be 1:3.
(3) the volumes calculated are not captured
(4) the volumes calculated are not printed
```{r}
volume_vector <- function(r) {
  volumes = c()
  for (power in 1:3){
    volume <- volume(r^power)
    print(volume)
    
    volumes = c(volumes, volume)
  }
  print("Volume of the spheres with radius r, r^2, r^3:")
  volumes
}
```

## Run volume_vector(r) and print the volumes of the sphere with radius r, r^2, and r^3
```{r}
r <- 2
volume_vector(r)
```



